---
title: "README"
author: "Mohsen Soltanifar"
date: "03/08/2022"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# descfars

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/MohsenSoltanifar/descfarspkg.svg?branch=master)](https://travis-ci.com/MohsenSoltanifar/descfarspkg)
<!-- badges: end -->

The goal of descfarspkg is to  present a set  of functions that presents descriptive statistics and plots for FARS 2013-2015 data.


## Installation

You can install the development version of descfarspkg with:

``` {r, warning=FALSE, eval=F,   message=FALSE}
# install.packages("devtools")
devtools::install_github("MohsenSoltanifar/descfarspkg")
```

## Example:  Total monthly accidents

This function gets the year in the dataset and returns a tibble datamatrix of two columns showing the counts of fatalities by month: year: 2015.

```{r, warning=FALSE, eval=F,   message=FALSE}
library(descfarspkg)
years <- c(2015)
fars_summarize_years(years)
```




