---
title: "descfarspkg_vignette"
author: "[Mohsen Soltanifar](https://github.com/MohsenSoltanifar/)"
date: "August 03, 2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{descfarspkg_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r , warning=FALSE, eval=F}
library(descfarspkg)
```
#(1) Package Description

The `descfarspkg` package presents descriptive statistics from Fatality Analysis Reporting System (FARS) data in 2012-2015 from the [National Highway Traffic Safety Administration](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars).

 


##(2) Load Packages

```{r, warning=FALSE, eval=F}
library(descfarspkg)
```


##(3)Included data

Data files included within the package are:

```{r, warning=FALSE, eval=F}
list.files(system.file("extdata", package = "descfarspkg"))
```

##(4) Package "descfarspkg" Functions

###(4-1) Function `make_filename`

This function produces file name and path to the data files from the farsdata:

```{r, warning=FALSE, eval=F}
year <- 2015
make_filename(year)
```

###(4-2) Function `fars_read_years`

This function reads the data per given year and is used by `fars_summarize_years`

```{r, warning=FALSE, eval=F}
fars_read_years(2015)
```


###(4-3) Function `fars_summarize_years`

This function produces a descriptive statistics including annual frequency of accidents, by month.

```{r, warning=FALSE, eval=F}
fars_summarize_years(2015) 
```

###(4-4) Function `fars_map_state`

The function produces a given state map plot including its occurred accidents locations in a given year in the period 2013-2015.

```{r, warning=FALSE, eval=F}
state_num <- 10 # Delaware
year <- 2015
fars_map_state(state_num, year)
```




# Links:
* [Package descfarspkg GitHub](https://github.com/MohsenSoltanifar/descfarspkg)
